Article results

### 2022-07-08 analysis/article-results.Rmd
Tweaks to ridge

# Get cal slope and intercept
split(df_calplot_valid, ~ .imp) |> 
  map(.f = ~ glm(Mc_FailedFemoralApproach ~ lp_valid, family = binomial, data = .x)) |> 
  pool() |> 
  summary()

split(df_calplot_valid, ~ .imp) |> 
  map(.f = ~ glm(Mc_FailedFemoralApproach ~ offset(lp_valid), family = binomial, data = .x)) |> 
  pool() |> 
  summary()

@@

mod_combined <- validation_comb_lambdamin$model_fit
validation_comb_lambdamin$model_fit$lambda

@@

calplot_MI(
  imps_long = imps_combined,
  model = validation_comb_lambdamin$model_fit,
  impdat_ind = ".imp",
  model_formula = model_formula,
  height_hist = 0.2,
  startpos_hist = -0.25,
  knots = 5,
  n_bins = 200,
  xlim = c(0, 0.5),
  ylim = c(-0.25, 0.8)
) +
  theme_minimal()

@@

  # First apparent performance
  folds <- assign_crossval_folds(y = unique(imputations[[".id"]]), n_folds = n_folds)
  mod_orig <- run_lasso_glmnet(
    x = X_orig,
    y = y_orig,
    wts = wts_orig,
    foldid = folds[match(imputations[[".id"]], folds[["y"]]), "fold"],
    lambda_choice = lambda_choice
  )

mod_orig$lambda
calplot_MI(
  imps_long = imps_combined,
  model = mod_orig,
  impdat_ind = ".imp",
  model_formula = model_formula,
  height_hist = 0.2,
  startpos_hist = -0.25,
  knots = 3,
  n_bins = 200,
  xlim = c(0, 0.5),
  ylim = c(-0.25, 0.8)
) +
  theme_minimal() 
```

>>>>

# Get cal slope and intercept
split(df_calplot_valid, ~ .imp) |> 
  map(.f = ~ glm(Mc_FailedFemoralApproach ~ lp_valid, family = binomial, data = .x)) |> 
  mice::pool() |> 
  summary()

split(df_calplot_valid, ~ .imp) |> 
  map(.f = ~ glm(Mc_FailedFemoralApproach ~ offset(lp_valid), family = binomial, data = .x)) |> 
  mice::pool() |> 
  summary()

@@

mod_combined <- validation_comb_lambdamin$model_fit
validation_comb_lambdamin$model_fit$lambda
mod_combined$beta

@@

calplot_MI(
  imps_long = imps_combined,
  model = validation_comb_lambdamin$model_fit,
  impdat_ind = ".imp",
  model_formula = model_formula,
  height_hist = 0.2,
  startpos_hist = -0.25,
  knots = 5,
  n_bins = 200,
  xlim = c(0, 0.55),
  ylim = c(-0.25, 0.8)
) +
  theme_minimal()

@@

  folds <- assign_crossval_folds(y = unique(imputations[[".id"]]), n_folds = n_folds)
cross_val <- glmnet::cv.glmnet(
    x = X_orig,
    y = y_orig,
    weights = wts_orig,
    foldid = folds[match(imputations[[".id"]], folds[["y"]]), "fold"],
    family = "binomial", 
    alpha = 0
  )

plot(cross_val)

  # First apparent performance - no penalty..
mod <-glmnet::glmnet(
    x = X_orig,
    y = y_orig,
    weights = wts_orig,
    family = "binomial",
    #lambda = 0, # unpenalized
    lambda = cross_val$lambda.min,
    alpha = 0, #ridge
    intercept = TRUE
  )

hist(plogis(predict(mod, newx = X_orig)))
max(plogis(predict(mod, newx = X_orig)))
coef(mod)
coef(
  glm(model_formula, data = imps_combined, family = binomial())
)
calplot_MI(
  imps_long = imps_combined,
  model = mod,
  impdat_ind = ".imp",
  model_formula = model_formula,
  height_hist = 0.2,
  startpos_hist = -0.25,
  knots = 5,
  n_bins = 200,
  xlim = c(0, 1),
  ylim = c(-0.25, 1)
) +
  theme_minimal()

# No penalty
modo <- glm(
  model_formula, family = binomial(), data = imps_combined, weights = imps_combined$wts
)
```
